---
title: "analysis_ectodecomposers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r include =FALSE}
library(readr)
library(car)
library(Rlab)
library(vegan)
library(ggplot2)
library(dplyr)
library(tidyr)
```

#read in data
```{r}
datasetlist.rel.agar.15<-read_csv("../clean_data/SS_data_relabun_agar_15_1.5perc.rev.csv")
test.old.data<-read_csv("../clean_data/SS_data_relabun_agar_15_1.5perc.csv")
datasetlist.rel.agar.genus.15<-read_csv("../clean_data/SS_data_relabun__agar_genus_15.rev.csv")
Meta.data.spatial<-read_csv("../clean_data/Clean_spatial_study_metadata.csv")
taxsetlist.agar<-read_csv("../clean_data/clean_taxonimcdata_SFSI_SS_agar_1.5percrev.csv")
test.old.cluster<-read_csv("../clean_data/clean_taxonimcdata_SFSI_SS_agar_1.5perc.csv")
```


#create weight averages
```{r}
#using untransformed but centered MnP activity per site.. everything is in same rows so can just multiply the matrix

wae.15<-as.data.frame(colSums(Meta.data.spatial$MnP_gOM_centered*datasetlist.rel.agar.15)/colSums(datasetlist.rel.agar.15))
colnames(wae.15)<-c("Weight.aver")

wae.15.perox<-as.data.frame(colSums(Meta.data.spatial$Perox_gOM_centered*datasetlist.rel.agar.15)/colSums(datasetlist.rel.agar.15))
colnames(wae.15.perox)<-c("Weight.aver")

wae.15.mnpindep<-as.data.frame(colSums(Meta.data.spatial$MnPindep_gOM_centered*datasetlist.rel.agar.15)/colSums(datasetlist.rel.agar.15))
colnames(wae.15.mnpindep)<-c("Weight.aver")

wae.15.genera<-as.data.frame(colSums(Meta.data.spatial$MnP_gOM_centered*datasetlist.rel.agar.genus.15)/colSums(datasetlist.rel.agar.genus.15))
colnames(wae.15.genera)<-c("Weight.aver")

wae.15.genera.perox<-as.data.frame(colSums(Meta.data.spatial$Perox_gOM_centered*datasetlist.rel.agar.genus.15)/colSums(datasetlist.rel.agar.genus.15))
colnames(wae.15.genera.perox)<-c("Weight.aver")
```

##compare ecology to WAE
```{r}
#make wae table with ecology (saprotrophic or mycorrhizal)
wae.15.ecol<-wae.15
tax.wae<-taxsetlist.agar[which(taxsetlist.agar$`Cluster ID` %in% rownames(wae.15.ecol)),c(1,4,15,16)]
tax.wae<-tax.wae[match(rownames(wae.15.ecol),tax.wae$`Cluster ID`,),]
wae.15.ecol$Ecology<-tax.wae$Ecology
wae.15.ecol$ref<-tax.wae$Reference
wae.15.sorted<-wae.15.ecol[match(sort(wae.15.ecol$Weight.aver,decreasing = TRUE),wae.15.ecol$Weight.aver),]

wae.15.ecol.perox<-wae.15.perox
tax.wae.perox<-taxsetlist.agar[which(taxsetlist.agar$`Cluster ID` %in% rownames(wae.15.ecol.perox)),c(1,4,15,16)]
tax.wae.perox<-tax.wae.perox[match(rownames(wae.15.ecol.perox),tax.wae.perox$`Cluster ID`,),]
wae.15.ecol.perox$Ecology<-tax.wae.perox$Ecology
wae.15.ecol.perox$ref<-tax.wae.perox$Reference
wae.15.sorted.perox<-wae.15.ecol[match(sort(wae.15.ecol.perox$Weight.aver,decreasing = TRUE),wae.15.ecol.perox$Weight.aver),]
```


#permutation test of the weighted averages
```{r}
#adapted from https://towardsdatascience.com/permutation-test-in-r-77d551a9f891

permutation.test <- function(MnP, spec.data, test.stat, n){
  distribution=c()
  result=0
  for(i in 1:n){
    distribution[[i]]=colSums(sample(MnP,length(MnP),FALSE)*spec.data)/colSums(spec.data)
  }
  dist.p=as.data.frame(distribution)
  for(j in 1:nrow(test.stat)){
  result[j]=sum(dist.p[j,]>=test.stat[j,])/(n)
  } #not the abs value because I want only one side test... 
  return(list(result, distribution))#result,
}

permutation.test.reverse <- function(MnP, spec.data, test.stat, n){
  distribution=c()
  result=0
  for(i in 1:n){
    distribution[[i]]=colSums(sample(MnP,length(MnP),FALSE)*spec.data)/colSums(spec.data)
  }
  dist.p=as.data.frame(distribution)
  for(j in 1:nrow(test.stat)){
  result[j]=sum(dist.p[j,]<=test.stat[j,])/(n)
  } #not the abs value because I want only one side test... 
  return(list(result, distribution))#result,
}
```

#species level - MnP dep
```{r}
set.seed(13)

permtest.results.15 <- permutation.test(MnP =  Meta.data.spatial$MnP_gOM_centered, spec.data = datasetlist.rel.agar.15,test.stat = wae.15, 10000)

#plot Cort
hist(as.numeric(as.data.frame(permtest.results.15[[2]])[14,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15[which(rownames(wae.15)== "scata6546_71"),], lwd=3, col="red")

#plot suillus 
hist(as.numeric(as.data.frame(permtest.results.15[[2]])[80,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15[which(rownames(wae.15)== "scata6546_346"),], lwd=3, col="red")


wae.perm.results.15<-as.data.frame(cbind(colnames(datasetlist.rel.agar.15),p.adjust(permtest.results.15[[1]],method = "fdr",length(permtest.results.15[[1]])),permtest.results.15[[1]]))
wae.perm.results.15[which(wae.perm.results.15$V3 < 0.1),]
wae.perm.results.15$ID<-taxsetlist.agar[match(wae.perm.results.15$V1,taxsetlist.agar$`Cluster ID`),]$Reference
colnames(wae.perm.results.15)<-c("Cluster_ID","adjusted_p","p","ID")

wae.perm.results.15[order(wae.perm.results.15$p),]
```

#species level - total peroxidase
```{r}
set.seed(13)

permtest.results.15.perox <- permutation.test(MnP =  Meta.data.spatial$Perox_gOM_centered, spec.data = datasetlist.rel.agar.15,test.stat = wae.15.perox, 10000)

#plot Cort
hist(as.numeric(as.data.frame(permtest.results.15.perox[[2]])[13,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15.perox[which(rownames(wae.15.perox)== "scata6531_82"),], lwd=3, col="red")

#plot suillus 
hist(as.numeric(as.data.frame(permtest.results.15.perox[[2]])[68,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15.perox[which(rownames(wae.15.perox)== "scata6531_318"),], lwd=3, col="red")


wae.perm.results.15.perox<-as.data.frame(cbind(colnames(datasetlist.rel.agar.15),p.adjust(permtest.results.15.perox[[1]],method = "fdr",length(permtest.results.15.perox[[1]])),permtest.results.15.perox[[1]]))
wae.perm.results.15.perox[which(wae.perm.results.15.perox$V3 < 0.1),]
wae.perm.results.15.perox$ID<-taxsetlist.agar[match(wae.perm.results.15.perox$V1,taxsetlist.agar$`Cluster ID`),]$Reference
colnames(wae.perm.results.15.perox)<-c("Cluster_ID","adjusted_p","p","ID")

wae.perm.results.15.perox[order(wae.perm.results.15.perox$p),]
```
#check overlapping of MnP and perox total results
```{r}
sig.mnp<-wae.perm.results.15[which(wae.perm.results.15$p < 0.1),]
sig.mnp<-rbind(sig.mnp,wae.perm.results.15[which(wae.perm.results.15$Cluster_ID == "scata6546_429"),])
sig.perox<-wae.perm.results.15.perox[which(wae.perm.results.15.perox$p < 0.1),]
only.mnp<-setdiff(sig.mnp$Cluster_ID,sig.perox$Cluster_ID)
only.perox<-setdiff(sig.perox$Cluster_ID,sig.mnp$Cluster_ID)

overlap.ID<-sig.perox[which(sig.perox$Cluster_ID %in% sig.mnp$Cluster_ID),]
sig.species<-rbind(overlap.ID,sig.mnp[which(sig.mnp$Cluster_ID %in% only.mnp),],sig.perox[which(sig.perox$Cluster_ID %in% only.perox),])
sig.species$type<-c(rep("both",nrow(overlap.ID)),rep("mnp",length(only.mnp)),rep("perox",length(only.perox)))
sig.species

sig.species<-separate(sig.species, ID, c("ID","SI","SH"),sep = "/",extra = "merge")
sig.species<-separate(sig.species, ID, c("Genus","species","extra"),sep="_",extra="merge")
sig.species.rearrange<-sig.species[which(is.na(sig.species$SI)),c(1:5,7,8,6,9)]
sig.species<-sig.species[-which(is.na(sig.species$SI)),] #remove ones that I need to rearrange
colnames(sig.species.rearrange)<-colnames(sig.species) #switch back column names
sig.species<-rbind(sig.species,sig.species.rearrange)# add back rearranged
sig.species[5,5]<-"fulvescens_coll." ### these are very specific fixes!!!! always double check before running!!!
sig.species[18,5]<-"mucosus.alpinus.fennoscandicus.trivialis"
sig.species[20,5]<-"stuposa_coll."
sig.species[22,5]<-"aff.lubrica"
sig.species<-sig.species[,-which(colnames(sig.species) %in% c("extra","SI"))]
sig.species[18,6]<-"SH1503718.08FU"

#add ecology and AA2 in genus 
taxa.sig<-taxsetlist.agar[which(taxsetlist.agar$`Cluster ID` %in% sig.species$Cluster_ID),]
taxa.sig<-taxa.sig[match(sig.species$Cluster_ID,taxa.sig$`Cluster ID`),]
sig.species$ecology<-taxa.sig$Ecology

write_csv(sig.species,file = "../clean_data/WAE_results.sig.csv")
```

#make nice table
```{r}
wae.perm.results.15<-wae.perm.results.15[match(rownames(wae.15),wae.perm.results.15$Cluster_ID),]
wae.perm.results.15$WAE<- wae.15$Weight.aver #add WAE 
wae.perm.results.15<-wae.perm.results.15[,c(1,4,3,5)] #re-order
wae.perm.results.15$Ecology <- wae.15.ecol$Ecology #add ecology
wae.perm.results.15$rot<-if_else(grepl("Suillus|Thelephora",wae.perm.results.15$ID),"BR","unk")

#make presence/absence data set - so I can add occurance
datasetlist.rel.agar.15.p<-datasetlist.rel.agar.15 
datasetlist.rel.agar.15.p[datasetlist.rel.agar.15.p>0]<-1
wae.perm.results.15$Occurrence <- colSums(datasetlist.rel.agar.15.p)

write_csv(wae.perm.results.15,file = "../figures/WAE_results.csv")
```

#species level - opposite
```{r}
set.seed(13)

#this now tests in the opposite direction which taxa have lower WAE than expected by random... 
permtest.results.15.oppo <- permutation.test.reverse(MnP =  Meta.data.spatial$MnP_gOM_centered, spec.data = datasetlist.rel.agar.15,test.stat = wae.15, 10000)


#plot piloderma
hist(as.numeric(as.data.frame(permtest.results.15.oppo[[2]])[2,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15[which(rownames(wae.15)== "scata6531_18"),], lwd=3, col="red")

#plot serendipita
hist(as.numeric(as.data.frame(permtest.results.15.oppo[[2]])[27,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15[which(rownames(wae.15)== "scata6531_110"),], lwd=3, col="red")

wae.perm.results.15.oppo<-as.data.frame(cbind(colnames(datasetlist.rel.agar.15),p.adjust(permtest.results.15.oppo[[1]],method = "fdr",length(permtest.results.15.oppo[[1]])),permtest.results.15.oppo[[1]]))
wae.perm.results.15.oppo[which(wae.perm.results.15.oppo$V3 < 0.1),]
wae.perm.results.15.oppo$ID<-taxsetlist.agar[match(wae.perm.results.15.oppo$V1,taxsetlist.agar$`Cluster ID`),]$Reference
colnames(wae.perm.results.15.oppo)<-c("Cluster_ID","adjusted_p","p","ID")

wae.perm.results.15.oppo[order(wae.perm.results.15.oppo$p),]
```
#species level - opposite total perox
```{r}
set.seed(13)

#this now tests in the opposite direction which taxa have lower WAE than expected by random... 
permtest.results.15.oppo.perox <- permutation.test.reverse(MnP =  Meta.data.spatial$Perox_gOM_centered, spec.data = datasetlist.rel.agar.15,test.stat = wae.15.perox, 10000)


#plot piloderma
hist(as.numeric(as.data.frame(permtest.results.15.oppo[[2]])[2,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15[which(rownames(wae.15)== "scata6531_18"),], lwd=3, col="red")

#plot serendipita
hist(as.numeric(as.data.frame(permtest.results.15.oppo[[2]])[27,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15[which(rownames(wae.15)== "scata6531_110"),], lwd=3, col="red")

wae.perm.results.15.oppo.perox<-as.data.frame(cbind(colnames(datasetlist.rel.agar.15),p.adjust(permtest.results.15.oppo.perox[[1]],method = "fdr",length(permtest.results.15.oppo.perox[[1]])),permtest.results.15.oppo.perox[[1]]))
wae.perm.results.15.oppo.perox[which(wae.perm.results.15.oppo.perox$V3 < 0.1),]
wae.perm.results.15.oppo.perox$ID<-taxsetlist.agar[match(wae.perm.results.15.oppo.perox$V1,taxsetlist.agar$`Cluster ID`),]$Reference
colnames(wae.perm.results.15.oppo.perox)<-c("Cluster_ID","adjusted_p","p","ID")

wae.perm.results.15.oppo.perox[order(wae.perm.results.15.oppo.perox$p),]

```
#check overlapping of MnP and perox total results
```{r}
sig.mnp.oppo<-wae.perm.results.15.oppo[which(wae.perm.results.15.oppo$p < 0.1),]
sig.perox.oppo<-wae.perm.results.15.oppo.perox[which(wae.perm.results.15.oppo.perox$p < 0.1),]
only.mnp.oppo<-setdiff(sig.mnp.oppo$Cluster_ID,sig.perox.oppo$Cluster_ID)
only.perox.oppo<-setdiff(sig.perox.oppo$Cluster_ID,sig.mnp.oppo$Cluster_ID)

overlap.ID.oppo<-sig.perox.oppo[which(sig.perox.oppo$Cluster_ID %in% sig.mnp.oppo$Cluster_ID),]
sig.species.oppo<-rbind(overlap.ID.oppo,sig.mnp.oppo[which(sig.mnp.oppo$Cluster_ID %in% only.mnp.oppo),],sig.perox.oppo[which(sig.perox.oppo$Cluster_ID %in% only.perox.oppo),])
sig.species.oppo$type<-c(rep("both",nrow(overlap.ID.oppo)),rep("mnp",length(only.mnp.oppo)),rep("perox",length(only.perox.oppo)))
sig.species.oppo

sig.species.oppo<-separate(sig.species.oppo, ID, c("ID","SI","SH"),sep = "/",extra = "merge")
sig.species.oppo<-separate(sig.species.oppo, ID, c("Genus","species","extra"),sep="_",extra="merge")
sig.species.oppo.rearrange<-sig.species.oppo[which(is.na(sig.species.oppo$SI)),c(1:5,7,8,6,9)]
sig.species.oppo<-sig.species.oppo[-which(is.na(sig.species.oppo$SI)),] #remove ones that I need to rearrange
colnames(sig.species.oppo.rearrange)<-colnames(sig.species.oppo) #switch back column names
sig.species.oppo<-rbind(sig.species.oppo,sig.species.oppo.rearrange)# add back rearranged
sig.species.oppo[2,5]<-"aff.obtusus" ### these are very specific fixes!!!! always double check before running!!!
sig.species.oppo[5,5]<-"emetica.coll_atrorubens.betularum"
sig.species.oppo[6,5]<-"laccata_coll."
sig.species.oppo[7,5]<-"byrophila_coll."
sig.species.oppo[30,5]<-"laccata_coll."
sig.species.oppo[28,5]<-"butyracea.f.asema"
sig.species.oppo[36,5]<-"mammosus_spinosulus_glyciomus"
sig.species.oppo<-sig.species.oppo[,-which(colnames(sig.species.oppo) %in% c("extra","SI"))]
sig.species.oppo[5,6]<-"SH1509012.08FU,SH1509012.08FU"
sig.species.oppo[30,6]<-"SH1553002.08FU"
sig.species.oppo[36,6]<-"SH1519108.08FU"

#add ecology and AA2 in genus 
taxa.sig.oppo<-taxsetlist.agar[which(taxsetlist.agar$`Cluster ID` %in% sig.species.oppo$Cluster_ID),]
taxa.sig.oppo<-taxa.sig.oppo[match(sig.species.oppo$Cluster_ID,taxa.sig.oppo$`Cluster ID`),]
sig.species.oppo$ecology<-taxa.sig.oppo$Ecology

write_csv(sig.species.oppo,file = "../clean_data/WAE_results.oppo.sig.csv")

sig.mnp.oppo[which(sig.mnp.oppo$Cluster_ID %in% sig.perox.oppo$Cluster_ID),]
sig.perox.oppo[which(sig.perox.oppo$Cluster_ID %in% sig.mnp.oppo$Cluster_ID),]
```



#genus level WAE
```{r}
set.seed(13)

permtest.results.15.genera <- permutation.test(MnP =  Meta.data.spatial$MnP_gOM_centered, spec.data = datasetlist.rel.agar.genus.15,test.stat = wae.15.genera, 10000)

wae.perm.results.15.genera<-as.data.frame(cbind(colnames(datasetlist.rel.agar.genus.15),p.adjust(permtest.results.15.genera[[1]],method = "fdr",length(permtest.results.15.genera[[1]])),permtest.results.15.genera[[1]]))
wae.perm.results.15.genera[which(wae.perm.results.15.genera$V3 < 0.1),]
#wae.perm.results.15.genera$ID<-taxsetlist.agar[[1]][match(wae.perm.results.15.genera$V1,taxsetlist.agar[[2]]$`Cluster ID`),]$Reference
colnames(wae.perm.results.15.genera)<-c("ID","adjusted_p","p")#,"ID"


wae.perm.results.15.genera[match(sort(wae.perm.results.15.genera$p),wae.perm.results.15.genera$p),]

wae.15.genera$genus<-rownames(wae.15.genera)
wae.15.genera.sorted<- wae.15.genera[match(sort(wae.15.genera$Weight.aver,decreasing = TRUE),wae.15.genera$Weight.aver),]
wae.15.genera.sorted
```

#genus level WAE - total peroxidase
```{r}
set.seed(13)

permtest.results.15.genera.perox <- permutation.test(MnP =  Meta.data.spatial$Perox_gOM_centered, spec.data = datasetlist.rel.agar.genus.15,test.stat = wae.15.genera.perox, 10000)

hist(as.numeric(as.data.frame(permtest.results.15.genera.perox[[2]])[56,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15.genera.perox[which(rownames(wae.15.genera.perox)== "Hydnum"),], lwd=3, col="red")

hist(as.numeric(as.data.frame(permtest.results.15.genera.perox[[2]])[66,]), breaks=50, col='grey', main="Permutation Distribution", las=1, xlab='')
abline(v=wae.15.genera.perox[which(rownames(wae.15.genera.perox)== "Gautieria"),], lwd=3, col="red")


wae.perm.results.15.genera.perox<-as.data.frame(cbind(colnames(datasetlist.rel.agar.genus.15),p.adjust(permtest.results.15.genera.perox[[1]],method = "fdr",length(permtest.results.15.genera.perox[[1]])),permtest.results.15.genera.perox[[1]]))
wae.perm.results.15.genera.perox[which(wae.perm.results.15.genera.perox$V3 < 0.1),]
#wae.perm.results.15.genera.perox$ID<-taxsetlist.agar[[1]][match(wae.perm.results.15.genera.perox$V1,taxsetlist.agar[[2]]$`Cluster ID`),]$Reference
colnames(wae.perm.results.15.genera.perox)<-c("ID","adjusted_p","p")#,"ID"


wae.perm.results.15.genera.perox[match(sort(wae.perm.results.15.genera.perox$p),wae.perm.results.15.genera.perox$p),]

wae.15.genera.perox$genus<-rownames(wae.15.genera.perox)
wae.15.genera.sorted.perox<- wae.15.genera.perox[match(sort(wae.15.genera.perox$Weight.aver,decreasing = TRUE),wae.15.genera.perox$Weight.aver),]
wae.15.genera.sorted.perox
```

#check overlapping of MnP and perox total results
```{r}
sig.genus.mnp<-wae.perm.results.15.genera[which(wae.perm.results.15.genera$p < 0.1),]
sig.genus.perox<-wae.perm.results.15.genera.perox[which(wae.perm.results.15.genera.perox$p < 0.1),]
only.mnp.g<-setdiff(sig.genus.mnp$ID,sig.genus.perox$ID)
only.perox.g<-setdiff(sig.genus.perox$ID,sig.genus.mnp$ID)

overlap.ID.g<-sig.genus.perox[which(sig.genus.perox$ID %in% sig.genus.mnp$ID),]
sig.genus.genera<-rbind(overlap.ID.g,sig.genus.mnp[which(sig.genus.mnp$ID %in% only.mnp.g),],sig.genus.perox[which(sig.genus.perox$ID %in% only.perox.g),])
sig.genus.genera$type<-c(rep("both",nrow(overlap.ID.g)),rep("mnp",length(only.mnp.g)),rep("perox",length(only.perox.g)))
sig.genus.genera
```

#make nice table 
```{r}
wae.perm.results.15.genera$WAE<- wae.15.genera$Weight.aver #add WAE 
wae.perm.results.15.genera<-wae.perm.results.15.genera[,c(1,3,4)] #re-order and remove adjusted P

#make presence/absence data set - so I can add occurance
datasetlist.rel.agar.genus.15.p<-datasetlist.rel.agar.genus.15 
datasetlist.rel.agar.genus.15.p[datasetlist.rel.agar.genus.15.p>0]<-1
wae.perm.results.15.genera$Occurrence <- colSums(datasetlist.rel.agar.genus.15.p)

write_csv(wae.perm.results.15.genera,file = "../figures/WAE_genus_results.csv")
```

#check consistency of CCA and WAE results 
```{r}
#read in the MNP CCA scores 
MnP.CCA.1<-read_csv("../clean_data/MNP.CCA.scores.1.5percrev.csv")

which(MnP.CCA.1$...1 %in% taxsetlist.agar$`Cluster ID`) #length 160


MnP.CCA.1<-MnP.CCA.1[which(MnP.CCA.1$...1 %in% taxsetlist.agar$`Cluster ID`),]

MnP.CCA.1<-MnP.CCA.1[match(MnP.CCA.1$...1,rownames(wae.15)),]

plot(MnP.CCA.1$CCA1*-1,wae.15$Weight.aver)
text(MnP.CCA.1$CCA1*-1,wae.15$Weight.aver,labels = rownames(wae.15))

MnP.CCA.2<-read_csv("../clean_data/MNP.CCA.scores.residu.1.5percrev.csv")

which(MnP.CCA.2$...1 %in% taxsetlist.agar$`Cluster ID`) #length 160


MnP.CCA.2<-MnP.CCA.2[which(MnP.CCA.2$...1 %in% taxsetlist.agar$`Cluster ID`),]

MnP.CCA.2<-MnP.CCA.2[match(MnP.CCA.2$...1,rownames(wae.15)),]

plot(MnP.CCA.2$CCA1*-1,wae.15$Weight.aver)
text(MnP.CCA.2$CCA1*-1,wae.15$Weight.aver,labels = rownames(wae.15))
```

#write WAE list
```{r}
write.csv(wae.15,"../clean_data/wae.15.csv")
wae.15.genera$Genus<-rownames(wae.15.genera)
colnames(wae.15.genera)<-c("Weight.aver","Genus")
write.csv(wae.15.genera,"../clean_data/wae.15.genera.csv")
```

