---
title: "analysis_ectodecomposers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r include =FALSE}
library(readr)
library(car)
library(Rlab)
library(vegan)
library(ggplot2)
library(dplyr)
library(tidyr)
library(factoextra)
library(beepr)
library(corrgram)
library(lme4)
library(splitstackshape)
library(DHARMa)
library(ggfortify)
library(ggrepel)
library(MuMIn)
```


#read in data
```{r}
datasetlist.rel.sfsi<-read_csv("clean_data/SFSI_data_relabun_1.5perc_filtered.rev.csv")
datasetlist.rel.sfsi.ecm<-read_csv("clean_data/SFSI_data_relabun_ECM_1.5perc_filtered.rev.csv")
SFSI.soil.f2<-read_csv("clean_data/Clean_filtered_SFSI_soil_data.rev.csv")
```

#create scaled soil parameters
```{r}
#this centers and scales the variables because they are all of very different magnitude
SFSI.soil.sel<-SFSI.soil.f2%>% mutate_at(c("Bestandsalder","Bestandsalder_log","Tallandel","Granandel","Bjorkandel","CN_log","Temperatursumma","pH_H2O_log","NC","CN","Cstock","Cstock_log","Mn_Ac","Mn_Ac_sqrt"),list(scaled =scale))


#PCA of variables of interest
pca.sfsi<-prcomp(SFSI.soil.sel[,which(colnames(SFSI.soil.sel) %in% c("Bestandsalder_scaled","pH_H2O_log_scaled","Granandel_scaled","NC_scaled"))]) 
fviz_pca_biplot(pca.sfsi,invisible = "ind",axes = c(1,2))#,"Granandel_scaled"
fviz_pca_biplot(pca.sfsi,invisible = "ind",axes = c(1,3))#

SFSI.soil.sel$pc1<- pca.sfsi$x[,1]
SFSI.soil.sel$pc2<- pca.sfsi$x[,2]
SFSI.soil.sel$pc3<- pca.sfsi$x[,3]
SFSI.soil.sel$pc4<- pca.sfsi$x[,4]

#create binary age category
SFSI.soil.sel$Bestandsaldercat<-as.factor(if_else(between(SFSI.soil.sel$Bestandsalder,0,70),"young",if_else(between(SFSI.soil.sel$Bestandsalder,70,400),"old","miss"))) #a split at 49 would give half old and young... at 70 it is 73% young and 26% old

SFSI.soil.sel$Bestandsaldercat<-factor(SFSI.soil.sel$Bestandsaldercat,levels=c('young','old')) #re-order the variables

#create seq platform variable
SFSI.soil.sel$seqplat<-as.factor(if_else(SFSI.soil.sel$Taxar %in% c("2014","2015","2016"),1,2))

```


#create fungal miners guild and investigate covariates of forest properties
```{r}
##read in WAE results
WAE.results<-read_csv("clean_data/WAE_results.sig.csv")
WAE.ecto.decomposers<-WAE.results[which(WAE.results$ecology == "ECM"),]
#remove Suillus, Thelephora, ,sitotrema etc... that have no known evidence of peroxidases within genus 
WAE.ecto.decomposers<-WAE.ecto.decomposers[-which(WAE.ecto.decomposers$Genus %in% c("Suillus","Thelephora","Thelephoraceae","Tomentella","Tylospora","Sistotrema","Tomentellopsis")),]#

miner.taxa.sfsi<-datasetlist.rel.sfsi[,which(colnames(datasetlist.rel.sfsi) %in% WAE.ecto.decomposers$Cluster_ID)]
colnames(miner.taxa.sfsi)<-paste(WAE.ecto.decomposers$Genus,WAE.ecto.decomposers$species,sep = "_")

miner.taxa.sfsi.ecm<-datasetlist.rel.sfsi.ecm[,which(colnames(datasetlist.rel.sfsi.ecm) %in% WAE.ecto.decomposers$Cluster_ID)]
colnames(miner.taxa.sfsi.ecm)<-paste(WAE.ecto.decomposers$Genus,WAE.ecto.decomposers$species,"ecmprop",sep = "_")
  
miner.taxa.p.sfsi<-miner.taxa.sfsi
miner.taxa.p.sfsi[miner.taxa.p.sfsi>0]<-1 # change to presence absence if rel abun is greater than zero
miner.taxa.p.sfsi[sapply(miner.taxa.p.sfsi,is.numeric)]<-lapply(miner.taxa.p.sfsi[sapply(miner.taxa.p.sfsi,is.numeric)],as.factor) #switch to factor from numeric

#relative aundace of guild as proportion of whole fungal community
miner.guild.sfsi<-rowSums(miner.taxa.sfsi) #aggreate into guild 
miner.guild.p.sfsi<-miner.guild.sfsi
miner.guild.p.sfsi[miner.guild.p.sfsi>0]<-1 #guild presence absence
miner.guild.sqrt.sfsi<-sqrt(miner.guild.sfsi) #hellinger transformation of realtive abun data

#relative aundace of guild as proportion of only ectomycorrhizal community
miner.guild.sfsi.ecm<-rowSums(miner.taxa.sfsi.ecm) #aggreate into guild 
miner.guild.sfsi.ecm[is.na(miner.guild.sfsi.ecm)]<-0 #1 sample has 0 relative abundance of ecto fungi and replace these Nan with zero
miner.guild.p.sfsi.ecm<-miner.guild.sfsi.ecm
miner.guild.p.sfsi.ecm[miner.guild.p.sfsi.ecm>0]<-1#guild presence absence
miner.guild.sqrt.sfsi.ecm<-sqrt(miner.guild.sfsi.ecm)#hellinger transformation of realtive abun data
```

# niche variables
```{r}
#bind together soil data and guild data
sfsi.fungniche<-as.data.frame(cbind(miner.taxa.sfsi,miner.taxa.sfsi.ecm,miner.taxa.p.sfsi,miner.guild.p.sfsi,miner.guild.sfsi,miner.guild.sfsi.ecm,miner.guild.sqrt.sfsi,miner.guild.sqrt.sfsi.ecm,SFSI.soil.sel$Bestandsalder_scaled,SFSI.soil.sel$Bestandsalder_log_scaled,SFSI.soil.sel$Granandel_scaled,SFSI.soil.sel$pH_H2O_log_scaled,SFSI.soil.sel$NC_scaled,SFSI.soil.sel$Temperatursumma_scaled,SFSI.soil.sel$Taxar,SFSI.soil.sel$Bestandsaldercat,SFSI.soil.sel$Cstock_log_scaled,SFSI.soil.sel$Cstock_scaled,SFSI.soil.sel$seqplat,SFSI.soil.sel$Bestandsalder,SFSI.soil.sel$NC,SFSI.soil.sel$CN,SFSI.soil.sel$Bjorkandel,SFSI.soil.sel$Granandel,SFSI.soil.sel$Tallandel,SFSI.soil.sel$pH_H2O,SFSI.soil.sel$Mn_Ac_sqrt_scaled,SFSI.soil.sel$Mn_Ac_sqrt))#

#rename variables 
colnames(sfsi.fungniche)<-c(colnames(miner.taxa.sfsi),paste("ecm",colnames(miner.taxa.p.sfsi)),paste("p",colnames(miner.taxa.p.sfsi)),"miners.pres","miners.rel","miners.relecm","miners.relsqrt","miners.relsqrtecm","age","age_log","spruce","pH","NC","temp","year","agecat","Cstock_log","Cstock","Seqplat","unscaled_age","unscaled_NC","unscaled_CN","unscaled_birch","unscaled_spruce","unscaled_pine","unscaled_pH","Mn_sqrt","unscaled_Mn_sqrt")#

#make a pine/spruce categorical variable 
sfsi.fungniche$tree_dom<-if_else(sfsi.fungniche$unscaled_spruce >= 60,"Spruce",if_else(sfsi.fungniche$unscaled_pine >= 60,"Pine","mix"))
sfsi.fungniche.all<-sfsi.fungniche
sfsi.fungniche<-sfsi.fungniche[-which(sfsi.fungniche$tree_dom == "mix"),]
table(sfsi.fungniche$tree_dom)
#this removes 29 sites where pine and spruce 50/50 (or 50/40/10 because of birch)

corrgram(sfsi.fungniche[,which(colnames(sfsi.fungniche) %in% c("miners.pres","age","pH","NC","spruce","temp","Mn_sqrt"))],upper.panel = panel.conf,lower.panel = panel.fill)#

#split into spruce and pine
hist(sfsi.fungniche$spruce)
sfsi.spruce<-sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce" ),]
sfsi.pine<-sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine" ),]

pca.sfsi.fert.pine<-prcomp(sfsi.pine[,which(colnames(sfsi.pine) %in% c("NC","pH"))]) 
pca.sfsi.fert.spruce<-prcomp(sfsi.spruce[,which(colnames(sfsi.spruce) %in% c("NC","pH"))])
fviz_pca_biplot(pca.sfsi.fert.pine,axes = c(1,2))#,invisible = "ind"
#fviz_pca_biplot(pca.sfsi.fert,axes = c(2,3))#,invisible = "ind"
fviz_pca_biplot(pca.sfsi.fert.spruce,axes = c(1,2))#,invisible = "ind"
#fviz_pca_biplot(pca.sfsi.fert,axes = c(2,3))#,invisible = "ind"

sfsi.pine$fert.pca <-c(pca.sfsi.fert.pine$x[,1]*1)
sfsi.spruce$fert.pca <-c(pca.sfsi.fert.spruce$x[,1]*-1)

corrgram(sfsi.fungniche[,which(colnames(sfsi.fungniche) %in% c("NC","pH","miners.pres","age","spruce","temp"))],upper.panel = panel.conf,lower.panel = panel.fill)
corrgram(sfsi.pine[,which(colnames(sfsi.pine) %in% c("fert.pca","miners.pres","unscaled_age","temp","unscaled_Mn"))],upper.panel = panel.conf,lower.panel = panel.fill)
corrgram(sfsi.spruce[,which(colnames(sfsi.spruce) %in% c("fert.pca","miners.pres","unscaled_age","temp","unscaled_Mn"))],upper.panel = panel.conf,lower.panel = panel.fill)



pca.sfsi<-prcomp(sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% c("NC","pH","spruce","age"))]) 
#tiff("../figures/revised/PCA_age_NC_pH.tiff",width = 100,height = 100,res = 1000,units = "mm")
fviz_pca_biplot(pca.sfsi,axes = c(1,2),geom = "point",repel = T)

pca.sfsi.fert<-prcomp(sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% c("NC","pH"))]) 
#tiff("../figures/revised/PCA_age_NC_pH.tiff",width = 100,height = 100,res = 1000,units = "mm")
fviz_pca_biplot(pca.sfsi.fert,axes = c(1,2),geom = "point",repel = T)

sfsi.fungniche.all$fert.pca<-c(pca.sfsi.fert$x[,1]*-1)#switch direction of pca so that to right is increasing fertility 
```

#compare presence of guild between pine and spruce
```{r}
fisher.test(as.matrix(table(sfsi.fungniche[,which(colnames(sfsi.fungniche) %in% c("tree_dom","miners.pres"))])),or=1)
```

##GLMM of presence absence
```{r}
glm.pa<-glmer(miners.pres~age_log+I(age_log^2)+fert.pca+I(fert.pca^2)+(1|Seqplat),family = binomial(link = "logit"),data = sfsi.fungniche.all)#+I(fert.pca^2)
glm.pa<-glmer(miners.pres~agecat+fert.pca+(1|Seqplat),family = binomial(link = "logit"),data = sfsi.fungniche.all)#+I(fert.pca^2)
summary(glm.pa)
Anova(glm.pa)
r.squaredGLMM(glm.pa)

glm.pa.spruce<-glmer(miners.pres~age_log+fert.pca+(1|Seqplat),family = binomial(link = "logit"),data = sfsi.spruce)#+Mn+I(age_log^2)+I(fert.pca^2)
glm.pa.spruce<-glmer(miners.pres~agecat+fert.pca+(1|Seqplat),family = binomial(link = "logit"),data = sfsi.spruce)#+I(fert.pca^2)
summary(glm.pa.spruce)
Anova(glm.pa.spruce)
r.squaredGLMM(glm.pa.spruce)

glm.pa.pine<-glmer(miners.pres~age_log+I(age_log^2)+fert.pca+(1|Seqplat),family = binomial(link = "logit"),data = sfsi.pine)#+I(fert.pca^2)
glm.pa.pine<-glmer(miners.pres~agecat+fert.pca+(1|Seqplat),family = binomial(link = "logit"),data = sfsi.pine)
summary(glm.pa.pine)
Anova(glm.pa.pine)
r.squaredGLMM(glm.pa.pine)


#check assumption of the glm using DHARMA https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html
simulationOutput <- simulateResiduals(fittedModel = glm.pa.spruce, plot = F)
plot(simulationOutput)
simulationOutput <- simulateResiduals(fittedModel = glm.pa.pine, plot = F)
plot(simulationOutput)

```


#compare relative abundance between pine and spruce
```{r}
sfsi.pres<-sfsi.fungniche[-which(sfsi.fungniche$miners.pres == 0),] #this makes a dataset where only sites where at least one of the six ecto decomposers are present are kept

hist(sfsi.pres$miners.relecm)
sfsi.pres$miner.relecmlog<-log10(sfsi.pres$miners.relecm)#can now do a log transformation 
sfsi.pres$miner.rellog<-log10(sfsi.pres$miners.rel)
hist(sfsi.pres$miner.relecmlog)

spruce.v.pine<-lm(sfsi.pres$miner.rellog~ sfsi.pres$tree_dom)
summary(spruce.v.pine)
plot(spruce.v.pine)
anova(spruce.v.pine)
```


#create relative abun dataset with samples only where guild is present
```{r}
##remove samples where persence is zero
sfsi.pine.pres<-sfsi.pine[-which(sfsi.pine$miners.pres == 0),]
sfsi.spruce.pres<-sfsi.spruce[-which(sfsi.spruce$miners.pres == 0),]
#Russula rhodopus is not present in any pine forests

#transform 
hist(sfsi.spruce.pres$miners.relecm)
sfsi.spruce.pres$miner.relecmlog<-log10(sfsi.spruce.pres$miners.relecm)
hist(sfsi.spruce.pres$miner.relecmlog)

hist(sfsi.pine.pres$miners.relecm)
sfsi.pine.pres$miner.relecmlog<-log10(sfsi.pine.pres$miners.relecm)
hist(sfsi.pine.pres$miner.relecmlog)

hist(sfsi.spruce.pres$miners.rel)
sfsi.spruce.pres$miner.rellog<-log10(sfsi.spruce.pres$miners.rel)
hist(sfsi.spruce.pres$miner.rellog)

hist(sfsi.pine.pres$miners.rel)
sfsi.pine.pres$miner.rellog<-log10(sfsi.pine.pres$miners.rel)
hist(sfsi.pine.pres$miner.rellog)
```

##LMM of relative abundance in proportion to only ecto comm
```{r}
#pine
lm.relecm.pine<-lmerTest::lmer(miner.relecmlog~agecat+fert.pca+(1|Seqplat),data = sfsi.pine.pres,na.action = na.omit)#+ I(age_log^2)
summary(lm.relecm.pine)
lm.relecm.pine<-lmerTest::lmer(miner.relecmlog~age_log +fert.pca+(1|Seqplat),data = sfsi.pine.pres)
summary(lm.relecm.pine)
plot(lm.relecm.pine)
r.squaredGLMM(lmer(miner.relecmlog~agecat+fert.pca+(1|Seqplat),data = sfsi.pine.pres))
r.squaredGLMM(lmer(miner.relecmlog~age_log+fert.pca+(1|Seqplat),data = sfsi.pine.pres))

#spruce
lm.relecm.spruce<-lmerTest::lmer(miner.relecmlog~agecat+fert.pca+(1|Seqplat),data = sfsi.spruce.pres)#
summary(lm.relecm.spruce)
lm.relecm.spruce<-lmerTest::lmer(miner.relecmlog~age_log+fert.pca+(1|Seqplat),data = sfsi.spruce.pres)
summary(lm.relecm.spruce)
plot(lm.relecm.spruce)
r.squaredGLMM(lmer(miner.relecmlog~agecat+fert.pca+(1|Seqplat),data = sfsi.spruce.pres))
r.squaredGLMM(lmer(miner.relecmlog~age_log+fert.pca+(1|Seqplat),data = sfsi.spruce.pres))


```
###LMM with relative abundance proportional to total fungal comm
```{r}
 #pine
lm.rel.pine<-lmerTest::lmer(miner.rellog~agecat+fert.pca+(1|Seqplat),data = sfsi.pine.pres)#
summary(lm.rel.pine)
lm.rel.pine<-lmerTest::lmer(miner.rellog~age_log+fert.pca+(1|Seqplat),data = sfsi.pine.pres)
summary(lm.rel.pine)
plot(lm.rel.pine)
r.squaredGLMM(lmer(miner.rellog~agecat+fert.pca+(1|Seqplat),data = sfsi.pine.pres))
r.squaredGLMM(lmer(miner.rellog~age_log+fert.pca+(1|Seqplat),data = sfsi.pine.pres))

#spruce
lm.rel.spruce<-lmerTest::lmer(miner.rellog~agecat+fert.pca+(1|Seqplat),data = sfsi.spruce.pres)#
summary(lm.rel.spruce)
lm.rel.spruce<-lmerTest::lmer(miner.rellog~age_log+fert.pca+(1|Seqplat),data = sfsi.spruce.pres)
summary(lm.rel.spruce)
plot(lm.rel.spruce)
r.squaredGLMM(lmer(miner.rellog~agecat+fert.pca+(1|Seqplat),data = sfsi.spruce.pres))
r.squaredGLMM(lmer(miner.rellog~age_log+fert.pca+(1|Seqplat),data = sfsi.spruce.pres))

```


##testing individual ectomycorrhizal species
```{r}
#presence/absence 
list.pres.abs.miners.s<-list(c(colnames(sfsi.spruce[,21:30]))) #gives list of species names of this in spruce forests
list.pres.abs.miners.p<-list(c(colnames(sfsi.pine[,c(21:28,30)]))) #gives list of species names of this in pine forests
list.pres.abs.miners<-list(c(colnames(sfsi.fungniche.all[,21:30]))) #gives list of species names of this in all forests

#create empty lists for results 
glm.fert.results.pine<-list()
glm.fert.results.spruce<-list()
glm.fert.sum.pine<-list()
glm.fert.sum.spruce<-list()
glm.age.results.pine<-list()
glm.age.results.spruce<-list()
glm.age.sum.pine<-list()
glm.age.sum.spruce<-list()
glm.age.results.fungniche.all<-list()
glm.age.sum.fungniche.all<-list()
glm.fert.results.fungniche.all<-list()
glm.fert.sum.fungniche.all<-list()

#across all forest presence absence - testing with a polynomial term 
for (i in 1:10){
glm.age.results.fungniche.all[[i]]<-Anova(glm(unlist(sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% list.pres.abs.miners[[1]][[i]])]) ~ age_log+ I(age_log^2), family = "binomial", data= sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% c("age_log",list.pres.abs.miners[[1]][[i]]))]))
glm.age.sum.fungniche.all[[i]]<-summary(glm(unlist(sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% list.pres.abs.miners[[1]][[i]])]) ~ age_log+ I(age_log^2), family = "binomial", data= sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% c("age_log",list.pres.abs.miners[[1]][[i]]))]))

glm.fert.results.fungniche.all[[i]]<-Anova(glm(unlist(sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% list.pres.abs.miners[[1]][[i]])]) ~ fert.pca+I(fert.pca^2), family = "binomial", data= sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% c("fert.pca",list.pres.abs.miners[[1]][[i]]))]))
glm.fert.sum.fungniche.all[[i]]<-summary(glm(unlist(sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% list.pres.abs.miners[[1]][[i]])]) ~ fert.pca+I(fert.pca^2), family = "binomial", data= sfsi.fungniche.all[,which(colnames(sfsi.fungniche.all) %in% c("fert.pca",list.pres.abs.miners[[1]][[i]]))]))
}

# for pine forests - presence absence
for (i in 1:9){
glm.age.results.pine[[i]]<-Anova(glm(unlist(sfsi.pine[,which(colnames(sfsi.pine) %in% list.pres.abs.miners.p[[1]][[i]])]) ~ age_log, family = "binomial", data= sfsi.pine[,which(colnames(sfsi.pine) %in% c("age_log",list.pres.abs.miners.p[[1]][[i]]))]))
glm.age.sum.pine[[i]]<-summary(glm(unlist(sfsi.pine[,which(colnames(sfsi.pine) %in% list.pres.abs.miners.p[[1]][[i]])]) ~ age_log, family = "binomial", data= sfsi.pine[,which(colnames(sfsi.pine) %in% c("age_log",list.pres.abs.miners.p[[1]][[i]]))]))

glm.fert.results.pine[[i]]<-Anova(glm(unlist(sfsi.pine[,which(colnames(sfsi.pine) %in% list.pres.abs.miners.p[[1]][[i]])]) ~ fert.pca, family = "binomial", data= sfsi.pine[,which(colnames(sfsi.pine) %in% c("fert.pca",list.pres.abs.miners.p[[1]][[i]]))]))
glm.fert.sum.pine[[i]]<-summary(glm(unlist(sfsi.pine[,which(colnames(sfsi.pine) %in% list.pres.abs.miners.p[[1]][[i]])]) ~ fert.pca, family = "binomial", data= sfsi.pine[,which(colnames(sfsi.pine) %in% c("fert.pca",list.pres.abs.miners.p[[1]][[i]]))]))
}

# for spruce forests - presence absence
for (i in 1:10){
glm.age.results.spruce[[i]]<-Anova(glm(unlist(sfsi.spruce[,which(colnames(sfsi.spruce) %in% list.pres.abs.miners.s[[1]][[i]])]) ~ age_log, family = "binomial", data= sfsi.spruce[,which(colnames(sfsi.spruce) %in% c("age_log",list.pres.abs.miners.s[[1]][[i]]))]))
glm.age.sum.spruce[[i]]<-summary(glm(unlist(sfsi.spruce[,which(colnames(sfsi.spruce) %in% list.pres.abs.miners.s[[1]][[i]])]) ~ age_log, family = "binomial", data= sfsi.spruce[,which(colnames(sfsi.spruce) %in% c("age_log",list.pres.abs.miners.s[[1]][[i]]))]))

glm.fert.results.spruce[[i]]<-Anova(glm(unlist(sfsi.spruce[,which(colnames(sfsi.spruce) %in% list.pres.abs.miners.s[[1]][[i]])]) ~ fert.pca, family = "binomial", data= sfsi.spruce[,which(colnames(sfsi.spruce) %in% c("fert.pca",list.pres.abs.miners.s[[1]][[i]]))]))
glm.fert.sum.spruce[[i]]<-summary(glm(unlist(sfsi.spruce[,which(colnames(sfsi.spruce) %in% list.pres.abs.miners.s[[1]][[i]])]) ~ fert.pca, family = "binomial", data= sfsi.spruce[,which(colnames(sfsi.spruce) %in% c("fert.pca",list.pres.abs.miners.s[[1]][[i]]))]))
}

glm.age.results.pine
glm.age.results.spruce
glm.age.sum.pine
glm.age.sum.spruce
glm.fert.results.pine
glm.fert.results.spruce
glm.fert.sum.pine
glm.fert.sum.spruce
glm.age.results.fungniche.all
glm.age.sum.fungniche.all
glm.fert.results.fungniche.all
glm.fert.sum.fungniche.all


```


#compare the individual species in pine or spruce 
```{r}
list.pres.abs.miners.all<-list(c(colnames(sfsi.pres[,21:30]))) #only in sites where at least one species is present 
fisher.age.results.all<-list()

for (i in 1:10){
fisher.age.results.all[[i]]<-fisher.test(as.matrix(table(sfsi.pres[,which(colnames(sfsi.pres) %in% c("tree_dom",list.pres.abs.miners.all[[1]][[i]]))])),or=1)
}

fisher.age.results.all
```



##correct p_values
```{r}
p.value.pine.list.glm.fert<-list()
p.value.spruce.list.glm.fert<-list()
p.value.pine.list.glm.age<-list()
p.value.spruce.list.glm.age<-list()
p.value.spruce.v.pine.fisher<-list()

#extract p values
for( i in 1:10){
p.value.spruce.list.glm.age[[i]]<-glm.age.results.spruce[[i]]$`Pr(>Chisq)`
p.value.spruce.list.glm.fert[[i]]<-glm.fert.results.spruce[[i]]$`Pr(>Chisq)`
p.value.spruce.v.pine.fisher[[i]]<-fisher.age.results.all[[i]]$p.value
}
for( i in 1:9){
p.value.pine.list.glm.age[[i]]<-glm.age.results.pine[[i]]$`Pr(>Chisq)`
p.value.pine.list.glm.fert[[i]]<-glm.fert.results.pine[[i]]$`Pr(>Chisq)`
  }

p.adjust(unlist(p.value.pine.list.glm.age),method = "fdr")
p.adjust(unlist(p.value.spruce.list.glm.age),method = "fdr")
p.adjust(unlist(p.value.pine.list.glm.fert),method = "fdr")
p.adjust(unlist(p.value.spruce.list.glm.fert),method = "fdr")
p.adjust(unlist(p.value.spruce.v.pine.fisher),method = "fdr")
```
#info on group
```{r}
#how many of the SFSI sites is guild present in
nrow(sfsi.pres)/nrow(sfsi.fungniche)

#how many sites for each taxa
for (i in 1:10){ 
print(table(sfsi.fungniche[,which(colnames(sfsi.fungniche) == list.pres.abs.miners.all[[1]][[i]])]))
}
mean(c(77,81,49,20,27,32,58,29,6,19))/nrow(sfsi.fungniche)
sd(c(77,81,49,20,27,32,58,29,6,19))/nrow(sfsi.fungniche)
6/548
81/548

#what is the groups average rel abun when present
mean(sfsi.pres$miners.rel)
mean(sfsi.pres$miners.relecm)

#how many ectos were identified in SFSI samples selected
ncol(datasetlist.rel.sfsi.ecm)
```

#write file with JordProvNr needed for upload to SRA
```{r}
#the only difference between the full soil dataset and the set used for data analysis is I remove samples that have 50% pine and spruce - even split so need to go from 577 to 548 samples
SFSI.soil.sel$tree_dom<-if_else(SFSI.soil.sel$Granandel >= 60,"Spruce",if_else(SFSI.soil.sel$Tallandel >= 60,"Pine","miss")) 
SFSI.soil.sel<-SFSI.soil.sel[-which(SFSI.soil.sel$tree_dom == "miss"),]

#write to a metadata file with only the variables I will want to share
#NC, Ph, tall, gran, jordprovnr, bestandalder, 
write_csv(SFSI.soil.sel[,which(colnames(SFSI.soil.sel) %in% c("NC","pH_H2O","Tallandel","Granandel","JordprovNr","Bestandsalder","Taxar"))],"../clean_data/SFSI_metadata_SRA.csv")
```


#write files for plotting
```{r}
write_csv(sfsi.pine.pres,"clean_data/SFSI_pine_guildpresent.rev.csv")
write_csv(sfsi.spruce.pres,"clean_data/SFSI_spruce_guildpresent.rev.csv")
write_csv(sfsi.pine,"clean_data/SFSI_pine.rev.csv")
write_csv(sfsi.spruce,"clean_data/SFSI_spruce.rev.csv")
write_csv(sfsi.fungniche,"clean_data/SFSI_total.rev.csv")
write_csv(sfsi.fungniche.all,"clean_data/SFSI_total.plus.csv")
write_csv(sfsi.pres,"clean_data/SFSI_present.rev.csv")
```
