---
title: "spatial.MnP.autocorrelation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r include=FALSE}
library(readr)
library(car)
library(vegan)
library(ggpubr)
library(ggplot2)
library(dplyr)
library(lmerTest)
library(segmented)
```


#read in metdata
```{r inlcude= FALSE}
Meta.data.spatial<-read_csv("../clean_data/Clean_spatial_study_metadata.csv")
```

#Standardization using Zscores 
MnP dependant activity per gOM (or per m2) is taken to create a data set where there is a measurement for each corner of each triangle. These means that samples where they are corners of overlapping triangles the values are repeated at most twice. Values below zero are already converted to zero each sample is assessed to a triangle by a letter where sharing a letter means it is part of the same triangle, there should be three values for each triangle.

```{r echo = FALSE}
##add column indicating which should be repeated and how many times
Meta.data.spatial$ntimes<-if_else(Meta.data.spatial$core %in% c(2,4,6,8,9,10,12,14,16,18,19,21,23,25,27,28,29,31,33,35,37,38),1,2)
Meta.data.spatial<-as.data.frame(lapply(Meta.data.spatial,rep,Meta.data.spatial$ntimes))

#add triangle label
Meta.data.spatial$triangle<-rep(c("Q",rep("A",3),rep("B",3),rep("C",3),rep("D",3),"Q","R",rep("E",3),rep("F",3),rep("G",3),rep("H",3),"R",rep("I",3),rep("J",3),rep("K",3),rep("L",3),"R","Q",rep("M",3),rep("N",3),rep("O",3),rep("P",3)),12)

##triangle size relates to letters as follows: 0.1 m = D,H,L,P; 0.3m = C,G,K,O; 1m = B,F,J,N; 3m = A,E,I,M; 10m = Q ,R

#scale by site and compare 
Meta.data.spatial<- Meta.data.spatial %>% group_by(plot)%>% mutate_at(c("MnP_gOM.log"),list(MnP_gOM.log_scaled = scale))#this will over write the scaled MnP that was done when the values were not repeated - but it should be the same anyways

sd(Meta.data.spatial[Meta.data.spatial$plot == "Gimo",]$MnP_gOM.log_scaled) #should equal one 

hist(Meta.data.spatial$MnP_gOM.log_scaled)
```

#Create variance per triangle 
The variance of each triangle will be calculated as the standard deviation of the three points on already standardized data 

```{r echo =FALSE }
Meta.data.spatial$plot.tri<-as.factor(paste(Meta.data.spatial$plot,Meta.data.spatial$triangle)) # make site triangle combined factor
is.factor(Meta.data.spatial$plot.tri)

Meta.data.spatial<-Meta.data.spatial %>% group_by(plot.tri) %>% mutate(variance = sd(MnP_gOM.log_scaled)) 

hist(Meta.data.spatial$variance)

##triangle size relates to letters as follows: 0.1 m = D,H,L,P; 0.3m = C,G,K,O; 1m = B,F,J,N; 3m = A,E,I,M; 10m = Q, R

#create variable of triangle size 
Meta.data.spatial$tri.size <- if_else(Meta.data.spatial$triangle %in% c('D','H','L','P'), '0.1m',if_else(Meta.data.spatial$triangle %in% c('C','G','K','O'),'0.3m',if_else(Meta.data.spatial$triangle %in% c('B','F','J','N'),'1m',if_else(Meta.data.spatial$triangle %in% c('A','E','I','M'),'3m','10m'))))
Meta.data.spatial$tri.size<- as.factor(Meta.data.spatial$tri.size)
Meta.data.spatial$tri.size<-ordered(Meta.data.spatial$tri.size, levels=c("0.1m","0.3m","1m","3m","10m")) #order so that when plotted it is always in order of increasing triangle size 

#seperate variables site, site.triangle, size and variance into one dataset then remove the repeated values so we are assessing by triangle not by core

MnP.var<- as.data.frame(Meta.data.spatial[,c(3,4,5,29,31,30)])
MnP.var<- unique(MnP.var) 
length(MnP.var$plot.tri) # now the data set should only be 216 in length 18 triangles x 12 sites 

plot(MnP.var$tri.size,MnP.var$variance)

#visualize the differences in MnP by age and species
ggplot(MnP.var, aes(x=tri.size, y=variance, colour=age))+geom_boxplot()+theme_classic()
ggplot(MnP.var, aes(x=tri.size, y=variance, colour=species))+geom_boxplot()+theme_classic()
ggplot(MnP.var, aes(x=tri.size, y=variance, colour=species,shape=age))+geom_jitter(position = position_jitterdodge(0.3) )+theme_classic()
```

#Test linear model with the MnP first transformed before z_score and SD
```{r}
#test model
lm.log.var<-lm(variance ~tri.size +age + species + tri.size*age+ tri.size*species, data=MnP.var)

summary(lm.log.var)
plot(lm.log.var)

anova(lm.log.var) # nothing is significant
```
```{r echo = FALSE}
#plot the size logged and variance (logged MnP) as a regression with host interactation
# Add regression lines
ggplot(MnP.var, aes(x=tri.size.log, y=variance, color=species)) +geom_point(position = position_dodge(0.3)) + geom_smooth(method=NULL,se=TRUE,level=0.95) + theme_classic()+ labs(x="Triangle tri.size logged",y="Standard deviation of MnP/gOM logged")

ggplot(MnP.var, aes(x=tri.size.log, y=variance)) +geom_point(position = position_dodge(0.3)) + geom_smooth(method=NULL,se=TRUE,level=0.95) + theme_classic()

```
