---
title: "figures_fungal_niche"
output: html_document
date: "2023-10-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#read in packages
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(ggforce)
library(patchwork)
library(extrafont)
library(ggsignif)
```

#read in data
```{r}
sfsi.pine<-read_csv("../clean_data/SFSI_pine.csv")
sfsi.spruce<-read_csv("../clean_data/SFSI_spruce.csv")
```

###frequency plot overall 
```{r}
sfsi.pine$agebinned<-as.factor(if_else(between(sfsi.pine$unscaled_age,10,31),"10-31",if_else(between(sfsi.pine$unscaled_age,32,45),"32-45",if_else(between(sfsi.pine$unscaled_age,46,65),"46-65",if_else(between(sfsi.pine$unscaled_age,66,107),"66-107",if_else(between(sfsi.pine$unscaled_age,108,400),">108","miss"))))))

sfsi.spruce$agebinned<-as.factor(if_else(between(sfsi.spruce$unscaled_age,10,28),"10-28",if_else(between(sfsi.spruce$unscaled_age,29,46),"29-46",if_else(between(sfsi.spruce$unscaled_age,47,60),"47-60",if_else(between(sfsi.spruce$unscaled_age,61,108),"61-108",if_else(between(sfsi.spruce$unscaled_age,109,400),">109","miss"))))))

levellist.p<-list('10-31','32-45', '46-65', '66-107','>108')
levellist.s<-list('10-28','29-46', '47-60', '61-108','>109')

freq.pine<-c()
for(i in 1:5){
freq.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$agebinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="miners.pres")])/nrow(sfsi.pine[which(sfsi.pine$agebinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="miners.pres")])  
}

freq.pine<-data.frame(first_column= c(round(as.numeric(freq.pine[[1]]),digits = 2),round(as.numeric(freq.pine[[2]]),digits = 2),round(as.numeric(freq.pine[[3]]),digits = 2),round(as.numeric(freq.pine[[4]]),digits = 2),round(as.numeric(freq.pine[[5]]),digits = 2)),second_column=c('10-31','32-45', '46-65', '66-107','>108'))

freq.pine$second_column<-factor(freq.pine$second_column,levels=c('10-31','32-45', '46-65', '66-107','>108'))

numsites.p<-c(118,109,114,110,113)

pine.freq<-ggplot(freq.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#2A9D8F", stat = "identity") +
  geom_text(aes(label = numsites.p,family="Times New Roman"), vjust = -0.3) + 
  xlab("")+
  ylab("Percent frequency")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()

freq.spruce<-c()
for(i in 1:5){
freq.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$agebinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="miners.pres")])/nrow(sfsi.spruce[which(sfsi.spruce$agebinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="miners.pres")])  
}

freq.spruce<-data.frame(first_column= c(round(as.numeric(freq.spruce[[1]]),digits = 2),round(as.numeric(freq.spruce[[2]]),digits = 2),round(as.numeric(freq.spruce[[3]]),digits = 2),round(as.numeric(freq.spruce[[4]]),digits = 2),round(as.numeric(freq.spruce[[5]]),digits = 2)),second_column=c('10-28','29-46', '47-60', '61-108','>109'))

freq.spruce$second_column<-factor(freq.spruce$second_column,levels=c('10-28','29-46', '47-60', '61-108','>109'))

numsites.s<-c(75,73,74,70,73)

spruce.freq<-ggplot(freq.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#275651", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.s,family="Times New Roman"), vjust = -0.3) + 
  xlab("Forest age")+
  ylab("Percent frequency")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()

#tiff("../figures/guild_frequencyplot.tiff",width = 8000,height = 10000,res = 1000)
pine.freq+spruce.freq+plot_layout(nrow = 2)+ plot_annotation(tag_levels = "A")

##binary age category of young and old 

sfsi.pine$agecat<-factor(sfsi.pine$agecat,levels=c('young','old'))
sfsi.spruce$agecat<-factor(sfsi.spruce$agecat,levels=c('young','old'))

levellist.p.b<-list('young','old')
levellist.s.b<-list('young','old')

binary.freq.pine<-c()
for(i in 1:2){
binary.freq.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$agecat == levellist.p.b[[i]]),which(colnames(sfsi.pine) =="miners.pres")])/nrow(sfsi.pine[which(sfsi.pine$agecat == levellist.p.b[[i]]),which(colnames(sfsi.pine) =="miners.pres")])  
}

binary.freq.pine<-data.frame(first_column= c(round(as.numeric(binary.freq.pine[[1]]),digits = 2),round(as.numeric(binary.freq.pine[[2]]),digits = 2)),second_column=c('young','old'))

binary.freq.pine$second_column<-factor(binary.freq.pine$second_column,levels=c('young','old'))

numsites.p.b<-c("n=360","n=204")

pine.binary.freq<-ggplot(binary.freq.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#2A9D8F", stat = "identity") +
  geom_text(aes(label = numsites.p.b,family="Times New Roman"), vjust = -0.3,) + 
  xlab("Forest age")+
  ylab("Frequency")+
  scale_y_continuous(limits = c(0,1))+
  geom_signif(comparisons = list(c("young", "old")), annotations = "*",y_position = 0.9)+
  theme_classic()+
  theme(text = element_text(size=12,family="Times New Roman"))

binary.freq.spruce<-c()
for(i in 1:2){
binary.freq.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$agecat == levellist.s.b[[i]]),which(colnames(sfsi.spruce) =="miners.pres")])/nrow(sfsi.spruce[which(sfsi.spruce$agecat == levellist.s.b[[i]]),which(colnames(sfsi.spruce) =="miners.pres")])  
}

binary.freq.spruce<-data.frame(first_column= c(round(as.numeric(binary.freq.spruce[[1]]),digits = 2),round(as.numeric(binary.freq.spruce[[2]]),digits = 2)),second_column=c('young','old'))

binary.freq.spruce$second_column<-factor(binary.freq.spruce$second_column,levels=c('young','old'))

numsites.s.b<-c("n=239","n=126")

spruce.binary.freq<-ggplot(binary.freq.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#275651", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.s.b,family="Times New Roman"), vjust = -0.3) + 
  xlab("Forest age")+
  ylab("Frequency")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(text = element_text(size=12,family="Times New Roman"))


#tiff("../figures/guild_binaryage_frequencyplot_pine.tiff",width = 85,height = 100,res = 1000,units = "mm")
pine.binary.freq+spruce.binary.freq+plot_layout(nrow = 2)+ plot_annotation(tag_levels = "A")
```

###frequency plot specific taxa
```{r}
freq.russ.spruce<-c()
for(i in 1:5){
freq.russ.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$agebinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Russula_aquosa")])/nrow(sfsi.spruce[which(sfsi.spruce$agebinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Russula_aquosa")])  
}

freq.russ.spruce<-data.frame(first_column= c(round(as.numeric(freq.russ.spruce[[1]]),digits = 2),round(as.numeric(freq.russ.spruce[[2]]),digits = 2),round(as.numeric(freq.russ.spruce[[3]]),digits = 2),round(as.numeric(freq.russ.spruce[[4]]),digits = 2),round(as.numeric(freq.russ.spruce[[5]]),digits = 2)),second_column=c('10-24','25-40', '41-51', '52-70','>71'))

freq.russ.spruce$second_column<-factor(freq.russ.spruce$second_column,levels=c('10-24','25-40', '41-51', '52-70','>71'))


russ.spruce.freq<-ggplot(freq.russ.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "darkred", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.s), vjust = -0.3) + 
  xlab("Forest age (years)")+
  scale_y_continuous(limits = c(0,1),breaks = c(0,0.25,0.5,0.75,1))+
  theme_classic()

freq.cort.pine<-c()
for(i in 1:5){
freq.cort.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$agebinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Cortinarius_semisanguineus")])/nrow(sfsi.pine[which(sfsi.pine$agebinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Cortinarius_semisanguineus")])  
}

freq.cort.pine<-data.frame(first_column= c(round(as.numeric(freq.cort.pine[[1]]),digits = 2),round(as.numeric(freq.cort.pine[[2]]),digits = 2),round(as.numeric(freq.cort.pine[[3]]),digits = 2),round(as.numeric(freq.cort.pine[[4]]),digits = 2),round(as.numeric(freq.cort.pine[[5]]),digits = 2)),second_column=c('10-34','35-46', '47-60', '61-95','>95'))

freq.cort.pine$second_column<-factor(freq.cort.pine$second_column,levels=c('10-34','35-46', '47-60', '61-95','>95'))


cort.pine.freq<-ggplot(freq.cort.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "darkred", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.p), vjust = -0.3) + 
  xlab("Forest age (years)")+
  scale_y_continuous(limits = c(0,1),breaks = c(0,0.25,0.5,0.75,1))+
  theme_classic()

freq.cort.c.spruce<-c()
for(i in 1:5){
freq.cort.c.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$agebinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Cortinarius_comptulus")])/nrow(sfsi.spruce[which(sfsi.spruce$agebinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Cortinarius_comptulus")])  
}

freq.cort.c.spruce<-data.frame(first_column= c(round(as.numeric(freq.cort.c.spruce[[1]]),digits = 2),round(as.numeric(freq.cort.c.spruce[[2]]),digits = 2),round(as.numeric(freq.cort.c.spruce[[3]]),digits = 2),round(as.numeric(freq.cort.c.spruce[[4]]),digits = 2),round(as.numeric(freq.cort.c.spruce[[5]]),digits = 2)),second_column=c('10-24','25-40', '41-51', '52-70','>71'))

freq.cort.c.spruce$second_column<-factor(freq.cort.c.spruce$second_column,levels=c('10-24','25-40', '41-51', '52-70','>71'))


cort.c.spruce.freq<-ggplot(freq.cort.c.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "darkred", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.s), vjust = -0.3) + 
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(0,1),breaks = c(0,0.25,0.5,0.75,1))+
  theme_classic()

freq.hyst.pine<-c()
for(i in 1:5){
freq.hyst.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$agebinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Hysterangium")])/nrow(sfsi.pine[which(sfsi.pine$agebinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Hysterangium")])  
}

freq.hyst.pine<-data.frame(first_column= c(round(as.numeric(freq.hyst.pine[[1]]),digits = 2),round(as.numeric(freq.hyst.pine[[2]]),digits = 2),round(as.numeric(freq.hyst.pine[[3]]),digits = 2),round(as.numeric(freq.hyst.pine[[4]]),digits = 2),round(as.numeric(freq.hyst.pine[[5]]),digits = 2)),second_column=c('10-34','35-46', '47-60', '61-95','>95'))

freq.hyst.pine$second_column<-factor(freq.hyst.pine$second_column,levels=c('10-34','35-46', '47-60', '61-95','>95'))


hyst.pine.freq<-ggplot(freq.hyst.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "darkred", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.p), vjust = -0.3) + 
  xlab("Forest age (years)")+
  ylab("")+
  scale_y_continuous(limits = c(0,1),breaks = c(0,0.25,0.5,0.75,1))+
  theme_classic()

russ.spruce.freq+cort.pine.freq+cort.c.spruce.freq+hyst.pine.freq

#tiff("../figures/frequencyplots_indivdualtaxa.tiff",width = 10000,height = 8000,res = 1000)
hyst.pine.freq+cort.c.spruce.freq+plot_layout(nrow = 2)+plot_annotation(tag_levels = "A")
```
##frequency plot overall fertility
```{r}
sfsi.pine$fertbinned<-as.factor(if_else(between(sfsi.pine$fert.pca,-3,-0.858936847),"lowest fert",if_else(between(sfsi.pine$fert.pca,-0.858936847,-0.443863327),"low fert",if_else(between(sfsi.pine$fert.pca,-0.443863327,-0.008901232),"mid-fert",if_else(between(sfsi.pine$fert.pca,-0.008901232,0.638079539),"high fert",if_else(between(sfsi.pine$fert.pca,0.638079539,6),"highest fert","miss"))))))

sfsi.spruce$fertbinned<-as.factor(if_else(between(sfsi.spruce$fert.pca,-3,-1.090116155),"lowest fert",if_else(between(sfsi.spruce$fert.pca,-1.090116155,-0.553973038),"low fert",if_else(between(sfsi.spruce$fert.pca,-0.553973038,0.009080885),"mid-fert",if_else(between(sfsi.spruce$fert.pca,0.009080885,0.904175886),"high fert",if_else(between(sfsi.spruce$fert.pca,0.904175886,5),"highest fert","miss"))))))

levellist.p<-list('lowest fert','low fert','mid-fert','high fert','highest fert')
levellist.s<-list('lowest fert','low fert','mid-fert','high fert','highest fert')

freq.pine<-c()
for(i in 1:5){
freq.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="miners.pres")])/nrow(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="miners.pres")])
}

freq.pine<-data.frame(first_column= c(round(as.numeric(freq.pine[[1]]),digits = 2),round(as.numeric(freq.pine[[2]]),digits = 2),round(as.numeric(freq.pine[[3]]),digits = 2),round(as.numeric(freq.pine[[4]]),digits = 2),round(as.numeric(freq.pine[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

freq.pine$second_column<-factor(freq.pine$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

numsites.p<-c(113,113,112,113,113)

pine.freq<-ggplot(freq.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#2A9D8F", stat = "identity") +
  geom_text(aes(label = numsites.p), vjust = -0.3) + 
  xlab("")+
  ylab("Percent frequency")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()

freq.spruce<-c()
for(i in 1:5){
freq.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$fertbinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="miners.pres")])/nrow(sfsi.spruce[which(sfsi.spruce$fertbinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="miners.pres")])  
}

freq.spruce<-data.frame(first_column= c(round(as.numeric(freq.spruce[[1]]),digits = 2),round(as.numeric(freq.spruce[[2]]),digits = 2),round(as.numeric(freq.spruce[[3]]),digits = 2),round(as.numeric(freq.spruce[[4]]),digits = 2),round(as.numeric(freq.spruce[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

freq.spruce$second_column<-factor(freq.spruce$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

numsites.s<-c(73,73,73,73,73)

spruce.freq<-ggplot(freq.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#275651", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  geom_text(aes(label = numsites.s), vjust = -0.3) + 
  xlab("NC")+
  ylab("Percent frequency")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()

#tiff("../figures/guild_frequencyplot_fert.tiff",width = 8000,height = 10000,res = 1000)
pine.freq+spruce.freq+plot_layout(nrow = 2)+ plot_annotation(tag_levels = "A")
```


##frequency plot specific taxa soil fertility
```{r}
means.cn.p<-c()
means.ph.p<-c()
means.cn.s<-c()
means.ph.s<-c()
for (i in 1:5){
means.cn.p[[i]]<-mean(sfsi.pine[sfsi.pine$fertbinned == levellist.p[[i]],]$unscaled_CN)
means.ph.p[[i]]<-mean(sfsi.pine[sfsi.pine$fertbinned == levellist.p[[i]],]$unscaled_pH)
means.cn.s[[i]]<-mean(sfsi.spruce[sfsi.spruce$fertbinned == levellist.s[[i]],]$unscaled_CN)
means.ph.s[[i]]<-mean(sfsi.spruce[sfsi.spruce$fertbinned == levellist.s[[i]],]$unscaled_pH)
}
means.cn.p
means.ph.p
means.cn.s
means.ph.s

gaut.freq.pine<-c()
for(i in 1:5){
gaut.freq.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Gautieria_monticola")])/nrow(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Gautieria_monticola")])
}

gaut.freq.pine<-data.frame(first_column= c(round(as.numeric(gaut.freq.pine[[1]]),digits = 2),round(as.numeric(gaut.freq.pine[[2]]),digits = 2),round(as.numeric(gaut.freq.pine[[3]]),digits = 2),round(as.numeric(gaut.freq.pine[[4]]),digits = 2),round(as.numeric(gaut.freq.pine[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

gaut.freq.pine$second_column<-factor(gaut.freq.pine$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

numsites.p<-c(113,113,112,113,113)

gaut.pine.freq<-ggplot(gaut.freq.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#2A9D8F", stat = "identity") +
  geom_text(aes(label = numsites.p), vjust = -0.3) + 
  xlab("")+
  ylab("Percent frequency")+
  annotate("text",x=0.6,y=-0.23,label="112.01",size=3)+
  annotate("text",x=1.5,y=-0.23,label="45.48",size=3)+
  annotate("text",x=2.5,y=-0.23,label="39.34",size=3)+
  annotate("text",x=3.5,y=-0.23,label="34.87",size=3)+
  annotate("text",x=4.5,y=-0.23,label="30.74",size=3)+
  annotate("text",x=5.4,y=-0.23,label="16.34",size=3)+
  #scale_y_continuous(limits = c(-0.05,1))+
  coord_cartesian(ylim = c(0,1),clip = "off")+
  theme_classic()+
  theme(text = element_text(size=9))#plot.margin = unit(c(1,1,5,2),"cm")

hsyt.freq.pine<-c()
for(i in 1:5){
hsyt.freq.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Hysterangium")])/nrow(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Hysterangium")])
}

hsyt.freq.pine<-data.frame(first_column= c(round(as.numeric(hsyt.freq.pine[[1]]),digits = 2),round(as.numeric(hsyt.freq.pine[[2]]),digits = 2),round(as.numeric(hsyt.freq.pine[[3]]),digits = 2),round(as.numeric(hsyt.freq.pine[[4]]),digits = 2),round(as.numeric(hsyt.freq.pine[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

hsyt.freq.pine$second_column<-factor(hsyt.freq.pine$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

hsyt.freq.pine$second_column<-ordered(hsyt.freq.pine$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))


hsyt.pine.freq<-ggplot(hsyt.freq.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#2A9D8F", stat = "identity") +
  #geom_text(aes(label = numsites.p), vjust = -0.3,size=3) + 
  xlab("")+
  ylab("")+
  geom_text(aes(x=1,y=-0.20,label="51 \n 3.4",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=2,y=-0.20,label="42 \n 3.5",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=3,y=-0.20,label="37 \n 3.6",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=4,y=-0.20,label="34 \n 3.8",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=5,y=-0.20,label="28 \n 4.3",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=6,y=-0.20,label="mean CN \n mean soil pH",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=3,y=1.1,label="Hysterangium aff. stoloniferum",family="Times New Roman",fontface=3),size=4,stat="unique")+
  annotate("segment",x = 1,xend = 5,y = 0.75, yend = 0.75)+
  annotate("text",label="*",x=3,y=0.8,size=3)+
  #scale_y_continuous(limits = c(-0.05,1))+
  coord_cartesian(ylim = c(0,1),clip = "off")+
  theme_classic()+
  theme(text = element_text(size=9,family="Times New Roman"),axis.text.x = element_blank(),plot.margin = unit(c(.06,.8,.6,0),"cm"))#

cort.se.freq.pine<-c()
for(i in 1:5){
cort.se.freq.pine[[i]]<-sum(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Cortinarius_semisanguineus")])/nrow(sfsi.pine[which(sfsi.pine$fertbinned == levellist.p[[i]]),which(colnames(sfsi.pine) =="p Cortinarius_semisanguineus")])
}

cort.se.freq.pine<-data.frame(first_column= c(round(as.numeric(cort.se.freq.pine[[1]]),digits = 2),round(as.numeric(cort.se.freq.pine[[2]]),digits = 2),round(as.numeric(cort.se.freq.pine[[3]]),digits = 2),round(as.numeric(cort.se.freq.pine[[4]]),digits = 2),round(as.numeric(cort.se.freq.pine[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

cort.se.freq.pine$second_column<-factor(cort.se.freq.pine$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

cort.se.freq.pine$second_column<-ordered(cort.se.freq.pine$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))


cort.se.pine.freq<-ggplot(cort.se.freq.pine, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#2A9D8F", stat = "identity") +
  #geom_text(aes(label = numsites.p), vjust = -0.3,size=3) + 
  xlab("")+
  ylab("Frequency")+
  geom_text(aes(x=1,y=-0.20,label="51 \n 3.4",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=2,y=-0.20,label="42 \n 3.5",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=3,y=-0.20,label="37 \n 3.6",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=4,y=-0.20,label="34 \n 3.8",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=5,y=-0.20,label="28 \n 4.3",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=6,y=-0.20,label="mean CN \n mean soil pH",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=3,y=1.1,label="Cortinarius semisanguineus sl.",family="Times New Roman",fontface=3),size=4,stat="unique")+
  #annotate("text",x=3,y=1.1,label="Cortinarius semisanguineus sl.",size=4,fontface="italic")+
  annotate("segment",x = 1,xend = 5,y = 0.75, yend = 0.75)+
  annotate("text",label="*",x=3,y=0.8,size=3)+
  #scale_y_continuous(limits = c(-0.05,1))+
  coord_cartesian(ylim = c(0,1),clip = "off")+
  theme_classic()+
  theme(text = element_text(size=9,family="Times New Roman"),axis.text.x = element_blank(),plot.margin = unit(c(0.06,.9,.6,0),"cm"))#plot.margin = unit(c(1,1,5,2),"cm")

hsyt.freq.spruce<-c()
for(i in 1:5){
hsyt.freq.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$fertbinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Hysterangium")])/nrow(sfsi.spruce[which(sfsi.spruce$fertbinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Hysterangium")])  
}

hsyt.freq.spruce<-data.frame(first_column= c(round(as.numeric(hsyt.freq.spruce[[1]]),digits = 2),round(as.numeric(hsyt.freq.spruce[[2]]),digits = 2),round(as.numeric(hsyt.freq.spruce[[3]]),digits = 2),round(as.numeric(hsyt.freq.spruce[[4]]),digits = 2),round(as.numeric(hsyt.freq.spruce[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

hsyt.freq.spruce$second_column<-factor(hsyt.freq.spruce$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

hsyt.freq.spruce$second_column<-ordered(hsyt.freq.spruce$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

numsites.s<-c(73,73,73,73,73)

hsyt.spruce.freq<-ggplot(hsyt.freq.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#275651", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  #geom_text(aes(label = numsites.s), vjust = -0.3,size=3) + 
  xlab("")+
  ylab("")+
  geom_text(aes(x=1,y=-0.20,label="39 \n 3.5",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=2,y=-0.20,label="34 \n 3.7",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=3,y=-0.20,label="30 \n 3.8",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=4,y=-0.20,label="28 \n 4.1",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=5,y=-0.20,label="22 \n 4.6",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=6,y=-0.20,label="mean CN \n mean soil pH",family="Times New Roman"),size=3,stat="unique")+
  annotate("segment",x = 1,xend = 5,y = 0.75, yend = 0.75)+
  annotate("text",label="*",x=3,y=0.8,size=3)+
  annotate("segment",x=1,xend = 5,y=-0.35,yend = -0.35,arrow=arrow(type = "open",length = unit(0.3,"cm")))+
  geom_text(aes(x=3,y=-0.4,label="Increasing soil fertility",family="Times New Roman"),stat="unique")+
  #scale_y_continuous(limits = c(-0.05,1))+
  coord_cartesian(ylim = c(0,1),clip = "off")+
  theme_classic()+
  theme(text = element_text(size=9,family="Times New Roman"),axis.text.x = element_blank(),plot.margin = unit(c(0,0.8,.9,0),"cm"))#
  

cort.se.freq.spruce<-c()
for(i in 1:5){
cort.se.freq.spruce[[i]]<-sum(sfsi.spruce[which(sfsi.spruce$fertbinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Cortinarius_semisanguineus")])/nrow(sfsi.spruce[which(sfsi.spruce$fertbinned == levellist.s[[i]]),which(colnames(sfsi.spruce) =="p Cortinarius_semisanguineus")])  
}

cort.se.freq.spruce<-data.frame(first_column= c(round(as.numeric(cort.se.freq.spruce[[1]]),digits = 2),round(as.numeric(cort.se.freq.spruce[[2]]),digits = 2),round(as.numeric(cort.se.freq.spruce[[3]]),digits = 2),round(as.numeric(cort.se.freq.spruce[[4]]),digits = 2),round(as.numeric(cort.se.freq.spruce[[5]]),digits = 2)),second_column=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

cort.se.freq.spruce$second_column<-factor(cort.se.freq.spruce$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))

cort.se.freq.spruce$second_column<-ordered(cort.se.freq.spruce$second_column,levels=c('lowest fert','low fert','mid-fert','high fert','highest fert'))


cort.se.spruce.freq<-ggplot(cort.se.freq.spruce, aes(x = second_column, y = first_column)) +
  geom_bar(fill = "#275651", stat = "identity") +
  scale_x_discrete(drop=FALSE)+
  #geom_text(aes(label = numsites.s), vjust = -0.3,size=3) + 
  xlab("")+
  ylab("Frequency")+
  #geom_link(aes(x=0.6,xend=5.4,y=-0.1,yend=-0.1,color="red"),arrow = arrow(),show.legend = FALSE)+
  #scale_color_gradient(low = "yellow",high = "red")+
  geom_text(aes(x=1,y=-0.20,label="39 \n 3.5",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=2,y=-0.20,label="34 \n 3.7",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=3,y=-0.20,label="30 \n 3.8",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=4,y=-0.20,label="28 \n 4.1",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=5,y=-0.20,label="22 \n 4.6",family="Times New Roman"),size=3,stat="unique")+
  geom_text(aes(x=6,y=-0.20,label="mean CN \n mean soil pH",family="Times New Roman"),size=3,stat="unique")+
  annotate("segment",x=1,xend = 5,y=-0.35,yend = -0.35,arrow=arrow(type = "open",length = unit(0.3,"cm")))+
  geom_text(aes(x=3,y=-0.4,label="Increasing soil fertility",family="Times New Roman"),stat="unique")+
  coord_cartesian(ylim = c(0,1),clip = "off")+
  theme_classic()+
  theme(text = element_text(size=9,family="Times New Roman"),axis.text.x = element_blank(),plot.margin = unit(c(0,.9,.9,0),"cm"))#plot.margin = unit(c(1,1,5,2),"cm")


gaut.pine.freq

cort.se.pine.freq+hsyt.pine.freq+cort.se.spruce.freq+hsyt.spruce.freq

#tiff("../figures/freq_hsyt_cort_fert.tiff",res = 1000,width = 175,height = 120,units = "mm")
cort.se.pine.freq+hsyt.pine.freq+cort.se.spruce.freq+hsyt.spruce.freq+plot_annotation(tag_levels = "A")
```



#read in data
```{r}
sfsi.pine.pres<-read_csv("../clean_data/SFSI_pine_guildpresent.csv")
sfsi.spruce.pres<-read_csv("../clean_data/SFSI_spruce_guildpresent.csv")
```

###relative abundance plot overall
```{r}
pine.plot<-ggplot(sfsi.pine.pres)+geom_point(aes(x=age_log,y=log10(sfsi.pine.pres$miners.rel)))+
  geom_smooth(aes(x=age_log,y=log10(sfsi.pine.pres$miners.rel)),method = "lm")+
  xlab("Forest age (years)")+
  ylab("Relative abundance of potential ectomycorrhizal decomposers (log scale) \n \n ")+
  #scale_x_continuous(breaks = c(10,50,100,150,200))+
  annotate("text",x=-2.5,y=0,label="100 %",size=3)+
  annotate("text",x=-2.5,y=-1,label="10 %",size=3)+
  annotate("text",x=-2.5,y=-2,label="1 %",size=3)+
  annotate("text",x=-2.5,y=-3,label="0.1 %",size=3)+
  #annotate("text",x=155,y= -0.1,label= "p=0.032")+
  #scale_y_continuous(limits = c(-3.3,0))+
  #coord_cartesian(clip = "off",xlim = c(0,210))+
  theme_classic()+
  theme(text=element_text(size = 12,family="Times New Roman"),axis.text.y = element_blank())
  

spruce.plot<-ggplot(sfsi.spruce.pres)+geom_point(aes(x=unscaled_age,y=log10(miners.relecm)))+
  geom_smooth(aes(x=unscaled_age,y=log10(miners.relecm)),method = "lm",se=FALSE)+
  xlab("Forest age (years)")+
  ylab("")+
  annotate("text",x=0,y=0,label="100 %")+
  annotate("text",x=0,y=-1,label="10 %")+
  annotate("text",x=0,y=-2,label="1 %")+
  annotate("text",x=0,y=-3,label="0.1 %")+
  #scale_x_continuous(limits=c(0,150),breaks = c(10,50,100,150,200))+
  annotate("text",x=100,y= -0.1,label= "p=0.438")+
  theme_classic()

pine.plot+spruce.plot

#tiff("../figures/guild_niche_age.tiff",res = 1000,width = 16000,height = 8000)
pine.plot+spruce.plot+plot_annotation(tag_levels = "A")

sfsi.pine.pres$agecat<-factor(sfsi.pine.pres$agecat,levels=c('young','old'))
sfsi.spruce.pres$agecat<-factor(sfsi.spruce.pres$agecat,levels=c('young','old'))

pine.plot.categ<-ggplot(sfsi.pine.pres)+geom_jitter(aes(x=agecat,y=log10(miners.relecm)),position = position_jitter(0.08))+
  stat_summary(aes(x=agecat,y=log10(miners.relecm)),fun.y =   "mean",geom = "point",colour="red",size=3)+
  stat_summary(aes(x=agecat,y=log10(miners.relecm)),fun.ymin = function(x) mean(x) - sd(x), fun.ymax = function(x) mean(x) + sd(x),geom = "linerange",colour="red",lwd=1)+
  xlab("Forest age")+
  ylab("")+
  annotate("text",x=-0,y=0,label="100 %",size=3)+
  annotate("text",x=-0.0001,y=-1,label="10 %",size=3)+
  annotate("text",x=-0.0001,y=-2,label="1 %",size=3)+
  annotate("text",x=-0.0001,y=-3,label="0.1 %",size=3)+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  scale_y_continuous(limits = c(-3.3,0))+
  theme_classic()+
  theme(text =element_text(size = 12,family="Times New Roman"),axis.text.y = element_blank())

pine.plot.categ.box<-ggplot(sfsi.pine.pres)+geom_boxplot(aes(x=agecat,y=log10(miners.relecm)))+
  stat_summary(aes(x=agecat,y=log10(miners.relecm)),fun.y =   "mean",geom = "point",colour="red",size=3)+
  stat_summary(aes(x=agecat,y=log10(miners.relecm)),fun.ymin = function(x) mean(x) - sd(x), fun.ymax = function(x) mean(x) + sd(x),geom = "linerange",colour="red",lwd=1)+
  xlab("Forest age")+
  ylab("")+
  annotate("text",x=-0,y=0,label="100 %",size=3)+
  annotate("text",x=-0.0001,y=-1,label="10 %",size=3)+
  annotate("text",x=-0.0001,y=-2,label="1 %",size=3)+
  annotate("text",x=-0.0001,y=-3,label="0.1 %",size=3)+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  scale_y_continuous(limits = c(-3.3,0))+
  theme_classic()+
  theme(text =element_text(size = 12,family="Times New Roman"),axis.text.y = element_blank())

spruce.plot.categ<-ggplot(sfsi.spruce.pres)+geom_jitter(aes(x=agecat,y=log10(miners.relecm)),position = position_jitter(0.08))+
  stat_summary(aes(x=agecat,y=log10(miners.relecm)),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=agecat,y=log10(miners.relecm)),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Forest age")+
  ylab("Potential guild \n relative abundance amoung ECM (logged) \n ")+
  annotate("text",x=-0.1,y=0,label="100 %",size=1.5)+
  annotate("text",x=-0.1,y=-1,label="10 %")+
  annotate("text",x=-0.1,y=-2,label="1 %")+
  annotate("text",x=-0.1,y=-3,label="0.1 %")+
  scale_y_continuous(limits = c(-3.3,0))+
  coord_cartesian(clip = "off")+
  theme_classic()+
  theme(axis.title=element_text(size = 12,family="Times New Roman"),axis.text.y = element_blank())

#tiff("../figures/guild_niche_age_pine_confint.tiff",res = 1000,width = 175,height = 120,units="mm")
pine.plot+pine.plot.categ+plot_layout(widths = c(4,2))+plot_annotation(tag_levels = "A")

spruce.plot.categ
```

###relative abundance plot specific taxa
```{r}
pine.cort.plot<-ggplot(sfsi.pine.pres[which(sfsi.pine.pres$`p Cortinarius_semisanguineus` == 1),])+geom_point(aes(x=unscaled_age,y=log10(`ecm Cortinarius_semisanguineus`)))+
  geom_smooth(aes(x=unscaled_age,y=log10(`ecm Cortinarius_semisanguineus`)),method = "lm")+
  xlab("Forest age (years)")+
  ylab("C.semi relative abundance \n amoung ECM (logged)")+
  scale_x_continuous(breaks = c(10,50,100,150,200))+
  annotate("text",x=0,y=0,label="100 %")+
  annotate("text",x=0,y=-1,label="10 %")+
  annotate("text",x=0,y=-2,label="1 %")+
  annotate("text",x=0,y=-3,label="0.1 %")+
  annotate("text",x=155,y= -0.1,label= "p=0.032")+
  theme_classic()

sfsi.pine.pres$agecat<-factor(sfsi.pine.pres$agecat,levels=c('young','old'))

pine.cort.plot<-ggplot(sfsi.pine.pres[which(sfsi.pine.pres$`p Cortinarius_semisanguineus` == 1),])+geom_jitter(aes(x=agecat,y=log10(`ecm Cortinarius_semisanguineus`)),position = position_jitter(0.08))+
  stat_summary(aes(x=agecat,y=log10(`ecm Cortinarius_semisanguineus`)),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=agecat,y=log10(`ecm Cortinarius_semisanguineus`)),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Forest age")+
  ylab("C.semisanguineus sl. relative abundance \n amoung ECM (logged)")+
  annotate("text",x=0.5,y=0,label="100 %")+
  annotate("text",x=0.5,y=-1,label="10 %")+
  annotate("text",x=0.5,y=-2,label="1 %")+
  annotate("text",x=0.5,y=-3,label="0.1 %")+
  annotate(geom = "text",label="62",x="young",y= -1,hjust=-2)+
  annotate(geom = "text",label="22",x="old",y=-1,hjust=-2)+
  #scale_y_continuous(limits = c(-3.2,0))+
  theme_classic()+
  theme(text = element_text(size = 14),)

pine.lact.plot<-ggplot(sfsi.pine.pres[which(sfsi.pine.pres$`p Lactarius_vietus` == 1),])+geom_jitter(aes(x=agecat,y=log(`ecm Lactarius_vietus`)),position = position_jitter(0.08))+
  stat_summary(aes(x=agecat,y=log(`ecm Lactarius_vietus`)),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=agecat,y=log(`ecm Lactarius_vietus`)),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Forest age")+
  ylab("L.vietus relative abundance \n amoung ECM (logged)")+
  annotate(geom = "text",label="16",x="young",y= -1,hjust=-2)+
  annotate(geom = "text",label="7",x="old",y=-1,hjust=-2)+
  scale_y_continuous(limits = c(-7,0))+
  theme_classic()

pine.cort.plot+pine.lact.plot

#tiff("../figures/fungniche.pine.tiff",res = 1000,width = 12000,height = 8000,units = "px")
pine.plot+pine.cort.plot+plot_layout(ncol = 2)+plot_annotation(tag_levels = "A")

#tiff("../figures/guild_niche_age_pine.tiff",res = 1000,width = 18000,height = 10000)
pine.plot+pine.plot.categ+pine.cort.plot+plot_layout(nrow = 1,widths = c(3,2,2))
```

#read in data
```{r}
sfsi.fungniche<-read_csv("../clean_data/SFSI_total.csv")
sfsi.pres<-read_csv("../clean_data/SFSI_present.csv")
```

###frequncey plot spruce vs pine
```{r}
freq.guild.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="miners.pres")])/564  
freq.guild.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="miners.pres")])/365 

freq.guild.p.v.s<-c(freq.guild.pine,freq.guild.spruce)
species<-c("Pine","Spruce")
freq.guild.p.v.s<-data.frame(freq.guild.p.v.s,species)

spr.v.pine.freq<-ggplot(freq.guild.p.v.s, aes(x = species, y = freq.guild.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("Dominant host species")+
  ylab("Percent frequency")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

spr.v.pine.freq
```
###frequncey plot spruce vs pine specific taxa
```{r}
freq.lact.all.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="p Lactarius_vietus")])/564
freq.lact.all.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="p Lactarius_vietus")])/365

freq.lact.p.v.s<-c(freq.lact.all.pine,freq.lact.all.spruce)
species<-c("Pine","Spruce")
freq.lact.p.v.s<-data.frame(freq.lact.p.v.s,species)

lact.spr.v.pine.freq<-ggplot(freq.lact.p.v.s, aes(x = species, y = freq.lact.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("")+
  ylab("Frequency")+
  annotate("text",x=1.5,y=1.0,label="L. vietus",size=4,fontface="italic")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

lact.spr.v.pine.freq

freq.gaut.all.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="p Gautieria_monticola")])/564
freq.gaut.all.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="p Gautieria_monticola")])/365 

freq.gaut.p.v.s<-c(freq.gaut.all.pine,freq.gaut.all.spruce)
species<-c("Pine","Spruce")
freq.gaut.p.v.s<-data.frame(freq.gaut.p.v.s,species)

gaut.spr.v.pine.freq<-ggplot(freq.gaut.p.v.s, aes(x = species, y = freq.gaut.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("")+
  ylab("")+
  annotate("text",x=1.5,y=1.0,label="G. monticola",size=4,fontface="italic")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

gaut.spr.v.pine.freq

freq.russ.all.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="p Russula_aquosa")])/564
freq.russ.all.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="p Russula_aquosa")])/365 

freq.russ.p.v.s<-c(freq.russ.all.pine,freq.russ.all.spruce)
species<-c("Pine","Spruce")
freq.russ.p.v.s<-data.frame(freq.russ.p.v.s,species)

russ.spr.v.pine.freq<-ggplot(freq.russ.p.v.s, aes(x = species, y = freq.russ.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("")+
  ylab("")+
  annotate("text",x=1.5,y=1.0,label="R. aquosa",size=4,fontface="italic")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

gaut.spr.v.pine.freq

freq.cortc.all.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="p Cortinarius_comptulus")])/564
freq.cortc.all.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="p Cortinarius_comptulus")])/365 

freq.cortc.p.v.s<-c(freq.cortc.all.pine,freq.cortc.all.spruce)
species<-c("Pine","Spruce")
freq.cortc.p.v.s<-data.frame(freq.cortc.p.v.s,species)

cortc.spr.v.pine.freq<-ggplot(freq.cortc.p.v.s, aes(x = species, y = freq.cortc.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("Dominant host species")+
  ylab("")+
  annotate("text",x=1.5,y=1.0,label="C. comptulus",size=4,fontface="italic")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

cortc.spr.v.pine.freq

freq.corts.all.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="p Cortinarius_semisanguineus")])/564 
freq.corts.all.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="p Cortinarius_semisanguineus")])/365 

freq.corts.p.v.s<-c(freq.corts.all.pine,freq.corts.all.spruce)
species<-c("Pine","Spruce")
freq.corts.p.v.s<-data.frame(freq.corts.p.v.s,species)

corts.spr.v.pine.freq<-ggplot(freq.corts.p.v.s, aes(x = species, y = freq.corts.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("Dominant host species")+
  ylab("")+
  annotate("text",x=1.5,y=1.0,label="C. semisanguineus sl.",size=4,fontface="italic")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

corts.spr.v.pine.freq

freq.hyst.all.pine<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Pine"),which(colnames(sfsi.fungniche) =="p Hysterangium")])/564
freq.hyst.all.spruce<-sum(sfsi.fungniche[which(sfsi.fungniche$tree_dom == "Spruce"),which(colnames(sfsi.fungniche) =="p Hysterangium")])/365 

freq.hyst.p.v.s<-c(freq.hyst.all.pine,freq.hyst.all.spruce)
species<-c("Pine","Spruce")
freq.hyst.p.v.s<-data.frame(freq.hyst.p.v.s,species)

hyst.spr.v.pine.freq<-ggplot(freq.hyst.p.v.s, aes(x = species, y = freq.hyst.p.v.s)) +
  geom_bar(fill = "seagreen", stat = "identity") +
  xlab("Dominant host species")+
  ylab("Frequency")+
  annotate("text",x=1.5,y=1.0,label="H. aff. stoloniferum",size=4,fontface="italic")+
  scale_y_continuous(limits = c(0,1))+
  theme_classic()+
  theme(axis.title=element_text(size = 12))

#tiff("../figures/fungniche.pine.vs.spruce_individ.tiff",res = 1000,width = 10000,height = 6000,units = "px")
lact.spr.v.pine.freq+gaut.spr.v.pine.freq+russ.spr.v.pine.freq+hyst.spr.v.pine.freq+corts.spr.v.pine.freq+cortc.spr.v.pine.freq+plot_annotation(tag_levels = "A")

```

###relative abundance plot spruce vs pine
```{r}
spr.v.pine.plot.categ<-ggplot(sfsi.pres)+geom_jitter(aes(x=tree_dom,y=log10(miners.relecm)),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=log10(miners.relecm)),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=log10(miners.relecm)),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of collective potential ectomycorrhizal decomposers \n amoung ectomycorrhizal fungi (logged) \n \n")+
  annotate("text",x=0.20,y=0,label="100 %",size=3)+
  annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  scale_y_continuous(limits = c(-3.5,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

#tiff("../figures/fungniche.pine.vs.spruce.tiff",res = 1000,width = 8000,height = 6000,units = "px")
spr.v.pine.freq+spr.v.pine.plot.categ+plot_annotation(tag_levels = "A")
```

```{r}
spr.v.pine.plot.categ.lact<-ggplot(sfsi.pres[which(sfsi.pres$`p Lactarius_vietus` > 0),])+geom_jitter(aes(x=tree_dom,y=Lactarius_vietus),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=Lactarius_vietus),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=Lactarius_vietus),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of Russula aquosa in sites where present (logged) \n \n")+
  #annotate("text",x=0.20,y=0,label="100 %",size=3)+
  #annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  #annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  #annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  #scale_y_continuous(limits = c(-3.2,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

spr.v.pine.plot.categ.gaut<-ggplot(sfsi.pres[which(sfsi.pres$`p Gautieria_monticola` > 0),])+geom_jitter(aes(x=tree_dom,y=Gautieria_monticola),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=Gautieria_monticola),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=Gautieria_monticola),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of Russula aquosa in sites where present (logged) \n \n")+
  #annotate("text",x=0.20,y=0,label="100 %",size=3)+
  #annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  #annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  #annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  #scale_y_continuous(limits = c(-3.2,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

spr.v.pine.plot.categ.russ<-ggplot(sfsi.pres[which(sfsi.pres$`p Russula_aquosa` > 0),])+geom_jitter(aes(x=tree_dom,y=Russula_aquosa),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=Russula_aquosa),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=Russula_aquosa),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of Russula aquosa in sites where present (logged) \n \n")+
  #annotate("text",x=0.20,y=0,label="100 %",size=3)+
  #annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  #annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  #annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  #scale_y_continuous(limits = c(-3.2,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

spr.v.pine.plot.categ.hyst<-ggplot(sfsi.pres[which(sfsi.pres$`p Hysterangium` > 0),])+geom_jitter(aes(x=tree_dom,y=Hysterangium),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=Hysterangium),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=Hysterangium),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of Russula aquosa in sites where present (logged) \n \n")+
  #annotate("text",x=0.20,y=0,label="100 %",size=3)+
  #annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  #annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  #annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  #scale_y_continuous(limits = c(-3.2,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

spr.v.pine.plot.categ.corts<-ggplot(sfsi.pres[which(sfsi.pres$`p Cortinarius_semisanguineus` > 0),])+geom_jitter(aes(x=tree_dom,y=Cortinarius_semisanguineus),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=Cortinarius_semisanguineus),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=Cortinarius_semisanguineus),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of Russula aquosa in sites where present (logged) \n \n")+
  #annotate("text",x=0.20,y=0,label="100 %",size=3)+
  #annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  #annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  #annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  #scale_y_continuous(limits = c(-3.2,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

spr.v.pine.plot.categ.cortc<-ggplot(sfsi.pres[which(sfsi.pres$`p Cortinarius_comptulus` > 0),])+geom_jitter(aes(x=tree_dom,y=Cortinarius_comptulus),position = position_jitter(0.08))+
  stat_summary(aes(x=tree_dom,y=Cortinarius_comptulus),fun.y =   "mean",geom = "point",colour="red")+
  stat_summary(aes(x=tree_dom,y=Cortinarius_comptulus),fun.data =   "mean_se",geom = "linerange",colour="red")+
  xlab("Dominant host species")+
  ylab("Relative abundance of Russula aquosa in sites where present (logged) \n \n")+
  #annotate("text",x=0.20,y=0,label="100 %",size=3)+
  #annotate("text",x=0.20,y=-1,label="10 %",size=3)+
  #annotate("text",x=0.20,y=-2,label="1 %",size=3)+
  #annotate("text",x=0.20,y=-3,label="0.1 %",size=3)+
  #scale_y_continuous(limits = c(-3.2,0))+
  coord_cartesian(clip = "off",xlim = c(1,2))+
  theme_classic()+
  theme(axis.title=element_text(size = 12),axis.text.y = element_blank())

spr.v.pine.plot.categ.lact+spr.v.pine.plot.categ.gaut+spr.v.pine.plot.categ.russ+spr.v.pine.plot.categ.hyst+spr.v.pine.plot.categ.corts+spr.v.pine.plot.categ.cortc
```

